Supporting Information: Thermal sensitivity across forest vertical profiles: patterns, mechanisms, and ecological implications

### 2021-10-01 vertical-thermal-review.Rmd
rearrange traits table
@NidhiVinod , please see if you like this before I make the images

Most leaf biochemical traits also vary across light and height gradients (Table `r table_leaf_traits`), both shaping and resulting from gradients in metabolism (see section 4, Table `r table_leaf_metabolism`).
Sun leaves have higher concentrations (per unit area) of elements such as nitrogen ($N_{area}$) and phosphorus ($P_{area}$) that are critical to leaf metabolism, including respiration [@meirLeafRespirationTwo2001;@weerasingheCanopyPositionAffects2014] and photosynthetic processes [@scartazzaInvestigatingEuropeanBeech2016; @niinemetsPhotosyntheticAcclimationSimultaneous2004; @weerasingheCanopyPositionAffects2014].
Increases in chlorophyll a/b ratios with height reflect the greater light availability in the upper canopy, while greater chlorophyll concentrations at lower heights within the canopy give shade leaves greater PAR absorptance efficiency (Table `r table_leaf_traits`).
Higher photosynthetic rates (per unit leaf area) and more frequent stomatal closure higher (see "Leaf gas exchange and its thermal sensitivity" section, Table `r table_leaf_metabolism`) result in lower intercellular CO~2~ concentrations and higher $\delta^{13}$C concentrations in leaf tissues (Table `r table_leaf_traits`).

>>>>

Most leaf biochemical traits also vary across light and height gradients (Table `r table_leaf_traits`), both shaping and resulting from gradients in metabolism (see section 4, Table `r table_leaf_metabolism`).
Sun leaves have higher concentrations (per unit area) of elements such as nitrogen ($N_{area}$) and phosphorus ($P_{area}$) that are critical to leaf metabolism, including respiration [@meirLeafRespirationTwo2001;@weerasingheCanopyPositionAffects2014] and photosynthetic processes [@scartazzaInvestigatingEuropeanBeech2016; @niinemetsPhotosyntheticAcclimationSimultaneous2004; @weerasingheCanopyPositionAffects2014].
Increases in chlorophyll a/b ratios with height reflect the greater light availability in the upper canopy, while greater chlorophyll concentrations at lower heights within the canopy give shade leaves greater PAR absorptance efficiency (Table `r table_leaf_traits`).
Higher photosynthetic rates (per unit leaf area) and more frequent stomatal closure higher (see section 4, Table `r table_leaf_metabolism`) result in lower intercellular CO~2~ concentrations and higher $\delta^{13}$C concentrations in leaf tissues (Table `r table_leaf_traits`).
